CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-12-04 codecheck-paper.tex
change heading levels
clarify types of checks

@@

\subsubsection*{Dimensions of CODECHECK processes}\label{dimensions-of-processes}

@@

\textbf{5. Open by default.}  By default, unless there are strong
reasons to the contrary (e.g., clinically-sensitive data), all code and
data, both from author and codechecker, will be made freely available, i.e., 
under open licenses, when the certificate is published. The code and data 
publication should follow community good practices.

\section*{Register}\label{register}
% count certificates: 
% curl https://codecheck.org.uk/register/stats.json
% -1 for Hathway-Goodman (no empty last line, so no -1 for the column headers needed)

We have a curated list of 22 certificates available at
\url{https://codecheck.org.uk/register}. These are a mixture of
reproductions of papers for a variety of reasons and fall into three themes:
(1) `classic' papers from computational neuroscience
(2) COVID-19 modelling preprints, and
(3) GIScience.  
The first theme was the initial set of papers used to explore the concept
of CODECHECK. The idea was to take very well known historical articles from a 
specific domain, in this case the work area of co-author S.~Eglen, possibly 
as as a conversation starter for potential collaborating journals.
The second theme is rather opportunistic. As the COVID-19 pandemic swept
over the whole Earth, we hoped to contribute a small part to science's answer
to the unknown virus. The checks were solicited through community interaction
%Several COVID-19 models have been done during the time of peer review of these papers,
and under our initative rather than requested from journal, but the certificate
has then been acknowledged/cited in the paper (LANCET/LSHTM). % TODO SJE: clarify references in brackets
The third theme represents co-author D.~N\"ust's work area.
Independent of CODECHECK, the \emph{Reproducible AGILE} Initiative \cite{reproducible_agile}
established a process for reproducing workflows at the AGILE conference
series. % TODO add reference to MUNIN talk
While using slightly different terms and infrastructue, e.g., `reproducibility
reports' are published on OSF, instead of certificates on Zenodo, the 
reproducibility reviews adhere to the codecheck principles.
Furthermore, two checks were completed as part of a peer review for a
GIScience journal.

@@

\subsubsection*{Tools and resources}\label{tools}

>>>>

\subsection*{Workflow and people}\label{workflow-people}

@@

\subsubsection*{Dimensions of CODECHECK workflows}\label{dimensions-of-workflows}

@@

\textbf{5. Open by default.}  By default, unless there are strong
reasons to the contrary (e.g., clinically-sensitive data), all code and
data, both from author and codechecker, will be made freely available, i.e., 
under open licenses, before or when the certificate is published.
The code and data  publication should follow community good practices.

\section*{Implementation}\label{register}

\subsection*{Register}\label{register}
% count certificates: 
% curl https://codecheck.org.uk/register/stats.json
% -1 for Hathway-Goodman (no empty last line, so no -1 for the column headers needed)

We have a curated list of 22 certificates available at
\url{https://codecheck.org.uk/register}. These are a mixture of
reproductions of papers for a variety of reasons and fall into three themes:
(1) `classic' papers from computational neuroscience
(2) COVID-19 modelling preprints, and
(3) GIScience.  
The first theme was the initial set of papers used to explore the concept
of CODECHECK. The idea was to take very well known historical articles from a 
specific domain, in this case the work area of co-author S.~Eglen, possibly 
as as a conversation starter for potential collaborating journals.
The second theme is rather opportunistic. As the COVID-19 pandemic swept
over the whole Earth, we hoped to contribute a small part to science's answer
to the unknown virus. The checks were solicited through community interaction
%Several COVID-19 models have been done during the time of peer review of these papers,
and under our initative rather than requested from journal, but the certificate
¸has then been acknowledged/cited in the paper (LANCET/LSHTM). % TODO SJE: clarify references in brackets
The third theme represents co-author D.~N\"ust's service as Reproducibility
Reviewer at the AGILE conference series.
Independent of CODECHECK, the \emph{Reproducible AGILE} Initiative \cite{reproducible_agile}
established a process for reproducing workflows at the AGILE conference
series \cite{nust_improving_2020}.
While using slightly different terms and infrastructue, e.g., ``reproducibility
reports'' are published on OSF instead of certificates on Zenodo, the 
reproducibility reviews adhere to the codecheck principles.
Furthermore, a small number of checks was completed as part of a peer reviews
for a GIScience journals.

@@

\subsection*{Tools and resources}\label{tools}
